---
output: github_document
---

#Installation 
install_github("https://github.com/stat545ubc-2023/DataRange", ref = "0.1.0")
```{r}
# install.packages("devtools")
devtools::install_github("https://github.com/stat545ubc-2023/DataRange")
```

#DESCRIPTION 
Package: DataRange
Type: Package
Title: Obtain the range of one column
Version: 0.1.0
Author: Mingming Zhang
Maintainer: Mingming Zhang <zhmm@student.ubc.ca>
Description: This function can compute the range of a column by using the column name from a dataset
License: MIT + file LICENSE
Encoding: UTF-8
Roxygen: list(markdown = TRUE)
RoxygenNote: 7.2.3
Imports: 
    stats,
    dplyr,
    tibble,
    tidyr,
    tidyselect
Suggests: 
    devtools,
    testthat (>= 3.0.0),
    tidyverse
Config/testthat/edition: 3

#Usage

#Example 1: In this example, use DataRange to obtain the range of column "texture_mean" in dataset "cancer_sample" as well as the NA number
```{r}
#show the minum and maximun values in "texture_mean" column in cancer_sample dataset
library(datateachr)
library(dplyr)
library(DataRange)
DataRange(cancer_sample,"texture_mean")
glimpse(DataRange(cancer_sample,"texture_mean"))
```

#Example 2: In this example, use DataRange to obtain the range of column "diameter" in the dataset of vancouver_trees
```{r}
diameter_range_Vtree<-DataRange(vancouver_trees,"diameter")
paste(diameter_range_Vtree)
```